%-------------------------
% Resume in Latex
% Author : Nigel Marshal
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{lato}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% Set the default text color to black for all text to ensure good contrast
\usepackage{xcolor}
\definecolor{textcolor}{HTML}{000000}

% Apply the text color
\color{textcolor}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----------Contact Info-----------

\begin{center}
  \textbf{\Huge \scshape Nigel Marshal} \\ \vspace{3pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:+123456789}{+123456789}
  $|$
  \faEnvelope \hspace{.5pt} \href{mailto:nigelmarshal@gmail.com}{nigelmarshal@gmail.com}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/NigelMarshal}{github.com/NigelMarshal}
  $|$
  \faGlobe \hspace{.5pt} \href{https://nigelmarshal.com}{nigelmarshal.com}
  $|$
\end{center}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Ajar}{Dubai, UAE}
{Software Engineer}{May 2022 -- Present}
\resumeItemListStart
\resumeItem{Directed major enhancements across 80\% of the entire platform as the Directly Responsible Individual (DRI), implementing key features with full CRUD functionality.}
\resumeItem{Led cross-platform integration between React \& Angular for feature parity, significantly elevating user experience and data interaction capabilities.}
\resumeItem{Incorporated automation testing with Playwright and GitHub actions workflows for CI/CD pipelines, expediting release cycles and reducing bug discovery time by 35\%. This improved code quality \& streamlined the deployment process.
}
\resumeItem{Implemented the integration of Facebook, Snapchat, and Google Tag Manager event tracking for KSA marketing campaigns, enhancing strategy with agencies to boost high-value client acquisitions by 20\%. and elevating campaign ROI.}
\resumeItemListEnd

\resumeSubheading
{Freelance Front-end Developer}{Dubai, UAE}
{Self-Employed}{April 2021 -- April 2022}
\resumeItemListStart
\resumeItem{Designed and developed SEO-optimized, responsive websites tailored to a diverse clientele, significantly enhancing user experience for small businesses and personal portfolios.}
\resumeItemListEnd

\resumeSubheading
{Abu Dhabi TAMM}{Abu Dhabi, UAE}
{Front-end Developer}{December 2019 -- March 2021}
\resumeItemListStart
\resumeItem{Designed and implemented 12+ government entity Sitecore websites for the Abu Dhabi Government TAMM Project, playing a key role in the public digitization efforts for the Abu Dhabi public as part of specialized SCRUM teams.}
\resumeItem{Constructed and maintained custom modular HTML5 and ES6/ES7 JavaScript components, allowing customizations for alignment with stakeholder branding themes and enhanced integration into multiple government Sitecore subsites.}
\resumeItem{Created and maintained thorough documentation for designed modular components and subsites, facilitating easy access and comprehension by 10+ remote teams and management via a development wiki on Jira Confluence.}
\resumeItemListEnd

\resumeSubheading
{dubizzle}{Dubai, UAE}
{Front-end Engineer for OLX MENA}{January 2019 -- November 2019}
\resumeItemListStart
\resumeItem{Served as the sole front-end developer for projects across eight MENA countries, including Lebanon, Egypt, and Oman.}
\resumeItem{Led the front-end implementation of the product’s paid ads subscription model, achieving a 50\% increase in user ad reach and significantly enhancing company revenue for the Middle East Region.}
\resumeItem{Collaborated on a strategic code migration from a custom PHP framework to React, working with a 5-member European remote team to boost codebase maintainability, enhance team efficiency and promote knowledge sharing.}
\resumeItemListEnd

\resumeSubheading
{Red Blue Blur Ideas (RBBi)}{Dubai, UAE}
{UX Specialist \& Developer}{September 2015 -- March 2018}
\resumeItemListStart
\resumeItem{Developed responsive websites using Wordpress, HTML5 and CSS3, ensuring top-quality solutions. Led outsourced teams for Banking and Real Estate projects, achieving over 95\% client satisfaction with timely, quality deliveries.}
\resumeItem{Implemented a hybrid approach as project manager and developer, overseeing client communications, updates, change requests and troubleshooting. This approach led to elevated client satisfaction and fostered enduring connections.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Heriot-Watt University}{Dubai, United Arab Emirates}
{Bachelor of Science in Computer Systems(Graduated with distinction)}{November 2015}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: JavaScript/TypeScript, HTML5, CSS3} \\
        \textbf{Frameworks/Libraries}{: React, Angular, Bootstrap, Tailwind, RxJS, Cypress, Playwright} \\
        \textbf{Tools}{: npm, git, RESTful APIs, Agile Methodologies}
        }}
\end{itemize}

\end{document}
